Multiple deprivation index using small area estimation methods: an application for the adult population in Colombia

### 2022-02-04 Paper_MPI_CEPAL/main.tex
Actualizado
autores

\NewDocumentCommand{\tens}{t_}
 {%
  \IfBooleanTF{#1}
   {\tensop}
   {\otimes}%
 }
\NewDocumentCommand{\tensop}{m}
 {%
  \mathbin{\mathop{\otimes}\displaylimits_{#1}}%
 }

\title{Multiple deprivation index using small area estimation methods: an application for the adult population in Colombia}
\author
{Author a $^{\ast}$, \\ 
Author b $^{\ast}$ $^\ast$, 
\\
\normalsize{$^\ast$ Affiliation a}\\
\normalsize{$^\ast$ $^\ast$ Affiliation b}
}

@@

Based on the new ``Multiple deprivation index" (MDI) for Latin American countries produced by the Economic Commission for Latin America and the Caribbean, this paper shows the case study of Colombia to obtain estimates of this index in small domains. This country has a recent population census (2018) providing most of the information required to compute the MDI at municipality level. However,  two of the indicators required to compute the index are not available in the census, namely: ``Employment-related income" and ``Lack of social security". Before computing the index, small area estimation (SAE) methods are implemented to obtain unit-level estimates for those specific indicators. Since two different SAE procedures are carried out, a parametric bootstrap algorithm is proposed to provide respective uncertainty measures.

@@

{{\bf \noindent Keywords}: Multidimensional poverty; Composite indicators; Empirical best predictor; Generalized linear mixed model}

\textcolor{red}{A discutir:}
\begin{itemize}
\item \textcolor{red}{Mencionamos el Índice de CEPAL? qué pasa si enviamos el abstract y el índice no se publica?}
\item \textcolor{red}{Como vamos a llamar estos dos indicadores: ``Employment-related income" y ``Lack of social security"? otras sugerencias?}
\item \textcolor{red}{No mencionar que es un índice solo para adultos ya que falta confirmación- revisar Título}
\item \textcolor{red}{Revisar las keywords}
\item \textcolor{red}{Mencionamos o no el bootstrap?}
\item \textcolor{red}{Orden y credenciales de cada autor}
\end{itemize}

@@

>>>>

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{authblk}
\NewDocumentCommand{\tens}{t_}
 {%
  \IfBooleanTF{#1}
   {\tensop}
   {\otimes}%
 }
\NewDocumentCommand{\tensop}{m}
 {%
  \mathbin{\mathop{\otimes}\displaylimits_{#1}}%
 }

\title{Multiple deprivation index using small area estimation methods: an application for the adult population in Colombia}

\author[1]{Andrés Gutiérrez-Rojas}
\author[2]{Alejandra Arias-Salazars}
\author[1]{Diego Lemus-Polanía}
\author[3]{Natalia Rojas-Perilla}
\author[1]{Xavier Mancero}
\affil[1]{Economic Commission for Latin America and the Caribbean}
\affil[2]{Freie Universität Berlin}
\affil[3]{United Arab Emirates University}

%\affil[1]{Statistics Division, Economic Commission for Latin America and the Caribbean}
%\affil[2]{Department of Economics, Freie Universität Berlin}
%\affil[3]{Department of Analytics in the Digital Era, United Arab Emirates University}

\renewcommand\Authands{ and }

@@

Based on the new ``Multiple deprivation index" (MDI) for Latin American countries produced by the Economic Commission for Latin America and the Caribbean, this paper shows the case study of Colombia to obtain estimates of this multidimensional index in small domains. This country has a recent population census (2018) providing most of the information required to compute the MDI at municipality level. However,  two of the indicators required to compute the index are not available in the census, namely: ``Employment-related income" and ``Lack of social security". Before computing the index, small area estimation (SAE) methods are implemented to obtain unit-level estimates for those specific indicators. Since two different SAE procedures are carried out, a parametric bootstrap algorithm is proposed to provide respective uncertainty measures.

@@

{{\bf \noindent Keywords}: Small area estimation; Multidimensional poverty; Composite indicators; Empirical best predictor; Generalized linear mixed model}

@@

\subsection{Metodología empleada}

-Describir cómo hacemos el proceso para unir las estimaciones al ``censo".

-Describir cómo se computa el índice.
